Survivable Set Connectivity

### 2015-05-13 draft.tex
added related work and context section in response to nitya's reply to karger

In this paper, we analyze the problem of Survivable Set Connectivity (SSC), a generalization of the classical Set Connectivity problem. Set connectivity is formulated as:
\begin{quote}
\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there is a path between $S_i$ and $T_i$ for each $i$. 
\end{quote}
In SSC, the problem is modified so that each pair of sets $(S_i,T_i)$ must be connected by $k_i$ paths, instead of just 1. More formally, the problem is:

@@

The paper is organized as follows. We first present a natural integer linear programming formulation of the problem. Then, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm. We also show a general rounding scheme, called RoundGKR, which our algorithm uses as a black box. Finally, we combine all these concepts together to present and analyze an approximation algorithm for SSC. 
%
%[ GIVE MORE EXAMPLES HERE ]
%
%As with many of these kinds of problems, SSC is $\mathsf{NP}$-hard. The common route taken in 6.856 has been to find polynomial time algorithms for approximations; however, in the case with SSC, it is $\mathsf{NP}$-hard to achieve a polylogarithmic approximation. 
%
%Another possible approach is therefore to relax the question. Instead of requiring at least $k$ edge-disjoint paths, we will allow some sets to have less than $k$ paths, but not too much less. We will present an approximation algorithm which outputs a subgraph of cost $O(polylog(n))$ times the optimum such that for each $(S_i, T_i)$ pairs, there are at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths between $S_i$ and $T_i$. 
%
%The approximation algorithm will follow the usual approach to approximation algorithms of this kind. We will first write the problem as an integer linear program, we solve the linear programming relaxation, and then we round the solution. 
%
%The analysis will be slightly different from the analysis shown in class. Usually, our randomized algorithm will return a feasible solution to the problem, and our analysis work is mostly to bound the cost. This was the case with max-sat, set-cover, and multi-commodity flows. In our case, we will show that the rounded solution will be close to the optimal, but we will work to show that the rounded solution is feasible.

>>>>

In this paper, we analyze the problem of Survivable Set Connectivity (SSC), a generalization of the classical Set Connectivity problem. Set connectivity is formulated as:
\begin{quote}
\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there is a path between $S_i$ and $T_i$ for each $i$. 
\end{quote}
In SSC, the problem is modified so that each pair of sets $(S_i,T_i)$ must be connected by $k_i$ paths, instead of just 1. More formally, the problem is:

@@

The paper is organized as follows. We first present a natural integer linear programming formulation of the problem. Then, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm. We also show a general rounding scheme, called RoundGKR, which our algorithm uses as a black box. Finally, we combine all these concepts together to present and analyze an approximation algorithm for SSC.

\subsection{Related Work and Context}

The paper by Chalermsook et al. is the first and (currently) only paper to consider the Survivable Set Connectivity problem \cite{ssc}. Therefore, we survey the only known approximation algorithm for the problem. Chalermsook et al. noted that the original Set Connectivity problem has a large body of prior work, but they found that the best techniques for solving Set Connectivity do not translate to the Survivable variant of the problem. Thus, we present Survivable Set Connectivity as a standalone problem, despite its obvious similarities to Set Connectivity.

At this time, it seems that Survivable Set Connectivity is only interesting from a theoretical standpoint, as a ``natural" generalization of Set Connectivity. It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.
